GiftGiver: The Gift Recommender \\ {\small AAI -- Instructor: Prof. Jane Hsu}

### 2011-06-22 paper/paper.tex
new pdf

\documentclass[11pt,twocolumn]{article}
\usepackage[left=1in,top=1in,right=1in,bottom=1in,nohead,foot=1cm]{geometry} 
\usepackage{aaai}
\usepackage{times}
\usepackage{tikz}
\usepackage{pgfplots}
\usepackage{amsmath,amssymb}
\usepackage{graphicx,psfrag}
\usepackage{amsthm} 
\usepackage{setspace}
\usepackage{comment}
\DeclareMathSymbol{\R}{\mathbin}{AMSb}{"52}

@@

\begin{tikzpicture}
    \begin{axis}[xlabel=Features, ylabel=Weight, legend style={at={(0.5, -0.2)}, anchor=north}]
    \addplot coordinates {(1, 4.583)};
    \addplot coordinates {(2, 4.917)};
    \addplot coordinates {(3, 4)};
    \addplot coordinates {(4, 4.06)};
    \addplot coordinates {(5, 4.31)};
    \addplot coordinates {(6, 3.75)};
    \addplot coordinates {(7, 4.583)};
    \addplot coordinates {(8, 2.75)};
    \addplot coordinates {(9, 4.25)};
    \addplot coordinates {(10, 2.583)};
    \addplot coordinates {(11, 2.583)};
    \addplot coordinates {(12, 1.583)};
    \legend{Occasion,Relationship,Price,Date,Interests,Receiver's Career,Receiver's Gender,Receiver's Religion,Receiver's Age,Sender's Career,Sender's Gender,Sender's Religion}
    \end{axis}
\end{tikzpicture}

@@

We have decided to take a feature matching approach of the recommendation system.
We analyze 60 gifts items and 3 common occasions and extract only 8 features.  
The features are:
\begin{tabular}{l l}
\hline\hline
Practical & Is it functional or just for decoration? \\
\hline
Meaningful & Is it has other meaning besides its function? \\
\hline
Beautiful & Is it good looking? \\
\hline
Trendy & Is it fashion? \\
\hline
Impersonal & Is it just for him/her or other people can use it? \\
\hline
Romantic & Is it present for love and sweet? \\
\hline
Geeky & Is it electrical? \\
\hline
Fun & Is it let you happy in a pure way? \\
\hline
\end{tabular}

Each gifts and occasion will have a vector of 8 features.  The value is normalized to[0,1].

Then the Vector will looks like below:
Gift     -> Book              [ 1.0, 0.6, 0.2, 0.4, 1.0, 0.0, 0.0, 0.6]
Occasion->Valentine’s day     [ 0.2, 1.0, 0.6, 0.2, 0.0, 1.0, 0.2, 0.2]

>>>>

\documentclass[11pt,twocolumn]{article}
\usepackage[left=1in,top=1in,right=1in,bottom=1in,nohead,foot=1cm]{geometry} 
\usepackage{aaai}
\usepackage{times}
\usepackage{tikz}
\usepackage{pgfplots}
\usepackage{amsmath,amssymb}
\usepackage{graphicx,psfrag}
\usepackage{amsthm} 
\usepackage{setspace}
\usepackage{comment}
\usepackage{algorithm}
\usepackage{algorithmic}
\DeclareMathSymbol{\R}{\mathbin}{AMSb}{"52}

@@

\begin{tikzpicture}
    \begin{axis}[xlabel=Features, ylabel=Weight, legend style={at={(0.5, -0.2)}, anchor=north}]
    \addplot coordinates {(1, 4.583)};
    \addplot coordinates {(2, 4.917)};
    \addplot coordinates {(3, 4)};
    \addplot coordinates {(4, 4.06)};
    \addplot coordinates {(5, 4.31)};
    \addplot coordinates {(6, 3.75)};
    \addplot coordinates {(7, 4.583)};
    \addplot coordinates {(8, 2.75)};
    \addplot coordinates {(9, 4.25)};
    \addplot coordinates {(10, 2.583)};
    \addplot coordinates {(11, 2.583)};
    \addplot coordinates {(12, 1.583)};
    \addplot coordinates {(13, 2.583)};
    \legend{Occasion,Relationship,Price,Date,Interests,Receiver's Career,Receiver's Gender,Receiver's Religion,Receiver's Age,Sender's Career,Sender's Gender,Sender's Religion, Sender's Age}
    \end{axis}
\end{tikzpicture}

@@

We have decided to take a feature matching approach of the recommendation system.
We analyze 60 gifts items and 3 common occasions and extract only 8 features.  
The features are:
\begin{tabular}{l l}
\hline\hline
Practical & Is it functional or just for decoration? \\
\hline
Meaningful & Is it has other meaning besides its function? \\
\hline
Beautiful & Is it good looking? \\
\hline
Trendy & Is it fashion? \\
\hline
Impersonal & Is it just for him/her or other people can use it? \\
\hline
Romantic & Is it present for love and sweet? \\
\hline
Geeky & Is it electrical? \\
\hline
Fun & Is it let you happy in a pure way? \\
\end{tabular}

Each object such as gift is defined by the feature vector. Each value is normalized from [0,1].
Occasion is also defined by the feature vector, however it is a special object, its existance
is essensial to our algorithms. Just as the same as the feature vectors defined in Shen's work~\cite{Shen}.

For example:
\begin{tabular}{l l}
\hline\hline
Book (Gift) & (1.0, 0.6, 0.2, 0.4, 1.0, 0.0, 0.0, 0.6) \\
\hline
Valentine’s day (Occasion) & (0.2, 1.0, 0.6, 0.2, 0.0, 1.0, 0.2, 0.2) \\
\end{tabular}

Occasion is treated differently than normal object. We sort our gift candidate from our sample pool of gifts of 20 by the mean square distance with target occasion that is specified in the UI by the users. Below the pseudocode described our first algorithm to sort gifts.

\begin{algorithm}
\caption{Mean Squared Distance sorting}
\label{mse}
\begin{algorithmic}
\STATE $X \Leftarrow x$
\end{algorithmic}
\end{algorithm}
